%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Change the font size of your document - 10pt, 12.1pt, etc.
\documentclass[letterpaper,11pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{kotex}

\usepackage{graphicx}
\graphicspath{ {images/}} %upload your signature to this file
%Change the margins to fit your CV/resume content
\usepackage[left=1in, right=1in, bottom=1.25in, top=1.25in]{geometry}


%Changes the page numbers - {arabic}=arabic numerals, {gobble}=no page numbers, {roman}=Roman numerals
\pagenumbering{gobble}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%% NAME OF APPLICANT %%%%%%%%%%%%%%%%%%%

\noindent  \LARGE{\textbf{Hyouk JANG}, 장 혁} \\
\vspace{-2ex} 
\hrule 
\normalsize

%%%%%%%%%%%%%%%%% CONTACT INFORMATION %%%%%%%%%%%%%%%%%
% Your email address, website, and Skype name are links to send email, open your website and add you on Skype. 
\begin{center}
\begin{tabular}{l l}
\href{hyoukjang.github.io}{https://hyoukjang.github.io} & \href{mailto:hyouk.a.jang@gmail.com}{hyouk.a.jang@gmail.com} \\
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%% MAIN BODY %%%%%%%%%%%%%%%%%%%%%%%%%%%
% The main body is contained in a tabular environment. To move sections onto the next page, simply end the tabular environment and begin a new tabular environment.

\noindent 
 \Large{Education}   \\ 
\noindent\rule{8cm}{0.4pt}\\
 \\
\normalsize\textbf{서울대학교 컴퓨터공학 석사} \\
Master of Science in Computer Science and Engineering, Seoul National University \\
Sep. 2016 to Feb. 2020. \\
\emph{Thesis : A Mobile VR Motion Controller with 6 DoF positioning using Light Polarization} \\
\emph{Advisor : Prof. Gunhee KIM} \\
\emph{Committee: Prof. Byoung-Tak ZHANG, Prof. U KANG, Prof. Gunhee KIM}
\\
\\
\textbf{고려대학교 전기전자전파공학사} \\
B.Eng in Electrical Engineering, Korea University \\ 
Feb. 2011 - Sep. 2015 \\
\\
\\
 \Large{Professional Experiences}   \\
 \noindent\rule{8cm}{0.4pt}\\
 \\
 \normalsize\textbf{{Data Scientist}, SOCAR} \\
 데이터 사이언티스트, (주)쏘카 \\
 Business development for the online used car retail service, CASTING by SOCAR and planned operations using data science. data modeling for vehicle selection, data-driven Inventory management, P\&L management, machine Learning based pricing modeling leading partnership with external sales channels, leading partnership with financial partners \\
March 2020 to Present \\
 \\
 \normalsize\textbf{{Software Engineer}, SOCAR} \\
 소프트웨어 엔지니어, (주)쏘카 \\
Android Mobile App Development \\
May 2019 to March 2020 \\
\\
\textbf{{CEO \& Co-founder}, POLARIANT, inc.} \\
공동창업자 및 대표이사, (주)폴라리언트 \\
May 2015 to Present \\
\textbf{\emph{acquired by SOCAR}} which is leading mobility platform holder in Korea in April, 2019. \\
\textbf{2019년 4월 쏘카에 피인수}\\
\\
\emph{POLARIANT opens a new era of precise indoor positioning through a technology that polarizes an indoor light source to find the 3-dimensional location and posture of objects. The core technology uses a small polarizing filter to be attached to any indoor lighting(POLAR) and a small sensor ‘ANT’ that receives the angle and distance data from the sensed light. It enable to make self-driving AGV(Automated Guided Vehicles) in smart factory, smart parking system which includes optimal path navigation for cars.}\\
\\
\textbf{President, NAEK YEHS(Young Engineers Honor Society)}\\
회장, 한국공학한림원 차세대공학리더 \\
Dec. 2015 to Dec. 2016 \\
\\
\emph{YEHS was founded by engineers from diverse universities to promote the exchange between the engineering students in various majors and to construct the long-term national scale network of engineers. It is sponsored by NAEK(National Academy fo Engineering KOREA). YEHS selects the members through the recommendation of the President of each university and the Dean of engineering college. Currently, students and graduates of a variety of Universities are involved. There are more than 1000 members from 30 universities.} \\
\\
\textbf{Co-chair, Student Committee of WEEF\&GEDC 2016, SEOUL}\\
학생위원회 위원장, 2016 세계공학교육포럼 및 세계공과대학장협의회 \\
2016 \\
\\
\emph{WEEF \& GEDC 2016, Seoul is The World Engineering Education Forum \& The Global Engineering Deans Council, 2016 Seoul. This Global forum was participated 41 countries 1,550 people (overseas participants 550). It was held Nov. 7 - Nov. 11 in COEX, Seoul}\\
\\
\\
 \Large{Awards}   \\
 \noindent\rule{8cm}{0.4pt}\\
 \\
\normalsize \textbf{Forbes 30 under 30 2020 Asia / Enterprise Technology} \\
2020 포브스 선정 30세 이하 아시아 차세대 리더 \\ 
April. 2020 \\
\\
\normalsize \textbf{Best Full Paper Award - Runner Up} \\
최우수 논문상 \\
25th ACM Symposium on Virtual Reality Software and Technology \\ 
Nov. 2019 \\
\\
\textbf{Talent of KOREA} \\
대한민국 인재상 \\
Dec. 2017 \\
\\
\textbf{Grand Excellence Prize, 1st NAEK Next Generation Award}\\
제 1회 한국공학한림원 차세대공학리더상 대상 \\
Dec. 2016 \\
\\
\textbf{The Excellence Award, Korea Computer Congress Paper Competition}\\
우수상, 한국컴퓨터종합학술대회 학부생 논문경진대회 \\
2014 \\
\\
\\

\clearpage
\setlength\parindent{0cm}
\pagenumbering{gobble} %cover letter should be one page, {gobble}=no page number


\end{document}

